Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
...

\def\HL{\textsf{HelpLine}}
\def\HF{\textsf{Helpfeel}}
\def\GIT{\texttt{git}}
\def\ES{\textsf{ExpandSearch}}
\def\SB{\textsf{Scrapbox}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % small quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}
\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}

@@

There have long been many researches on
intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people,
either by searching existing Web pages or 
by asking in user forums like StackOverflow\footnote{
  \textsf{https://stackoverflow.com/}
}.
Information on the net is rich these days, and we can easily
find somebody who can give good answers to our questions.
This is a good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like {\ES} is
preferable most of the time.

@@

\begin{verbatim}
    検索システムを選んでから検索キーワードを入力するのに慣れてしまっている
  この必要がないことを知ると驚きがある
 検索されやすいように工夫するとか馬鹿げてると
思うかもしれないか、ググって出なきゃ無いのと同じだということを考えると、
ある程度工夫することは意味があるし、自分が後でさがすときにも役に立つわけである
  ゲームのように記述を増やす工夫もできるかもしれない
  タイトルに迷ったら両方書くみたいな
 どこにある情報でもひとつのインタフェースでみつかるのは強烈に嬉しい

[[説得ポイント]]
 ExpandHelp
  自分が入力したキーワードが検索結果に出現する嬉しさ
 検索方法の統合
 ヘルプシステムの実績

[[関連システム / 参考文献]]
 普通の[https://en.wikipedia.org/wiki/Query_expansion クエリ拡張]
 Relevance Feedback
  検索パタンを増やすことに効果があるといえる
 [https://scrapbox.io/UIPedia/George_Furnas:_The_vocabulary_problem_in_human-system_communication Vocabulary problem]
 [文芸的プログラミング]
  ExpandHelp記述は文芸的プログラミングの一種だと思えばいい
  冗長な感じで書くといい
 [/Rubytips] の実例

日本語を入力すると英語のWikipediaがみつかることもある
 これはたぶん原文を翻訳したものを検索対象にしている
 これもDocument Expansionといえる

\end{verbatim}

\paragraph{Applications of ExpandSearch}

@@

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac1}
\end{figure}

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac2}
\end{figure}

\paragraph{Order of command and arguments}

@@

\paragraph{Usage of regular expressions}

>>>>

\def\HL{\textsf{HelpLine}}
\def\HF{\textsf{Helpfeel}}
\def\GIT{\texttt{git}}
\def\ES{\textsf{ExpandSearch}}
\def\SB{\textsf{Scrapbox}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{8pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{8pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % small quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}
\long\def\smallfont{\fontsize{8pt}{0pt}\selectfont}

@@

There have long been many researches on
intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people,
either by searching existing Web pages or 
by asking in user forums like StackOverflow\footnote{
  \ssf{https:{\slash}{\slash}stackoverflow.com{\slash}}
}.
Information on the net is rich these days, and we can easily
find somebody who can give good answers to our questions.
This is a good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like {\ES} is
preferable most of the time.

@@

%     検索システムを選んでから検索キーワードを入力するのに慣れてしまっている
%   この必要がないことを知ると驚きがある
%  検索されやすいように工夫するとか馬鹿げてると
% 思うかもしれないか、ググって出なきゃ無いのと同じだということを考えると、
% ある程度工夫することは意味があるし、自分が後でさがすときにも役に立つわけである
%   ゲームのように記述を増やす工夫もできるかもしれない
%   タイトルに迷ったら両方書くみたいな
%  どこにある情報でもひとつのインタフェースでみつかるのは強烈に嬉しい
% 
% [[説得ポイント]]
%  ExpandHelp
%   自分が入力したキーワードが検索結果に出現する嬉しさ
%  検索方法の統合
%  ヘルプシステムの実績
% 
% [[関連システム / 参考文献]]
%  普通の[https://en.wikipedia.org/wiki/Query_expansion クエリ拡張]
%  Relevance Feedback
%   検索パタンを増やすことに効果があるといえる
%  [https://scrapbox.io/UIPedia/George_Furnas:_The_vocabulary_problem_in_human-system_communication Vocabulary problem]
%  [文芸的プログラミング]
%   ExpandHelp記述は文芸的プログラミングの一種だと思えばいい
%   冗長な感じで書くといい
%  [/Rubytips] の実例
% 
% 日本語を入力すると英語のWikipediaがみつかることもある
%  これはたぶん原文を翻訳したものを検索対象にしている
%  これもDocument Expansionといえる

\subsection*{Other applications of ExpandSearch}

@@

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
  \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac1}
\end{figure}

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
  \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac2}
\end{figure}

\subsection*{Order of command and arguments}

@@

\subsection*{Usage of regular expressions}
